Tensor anisotropy as a tracer of cosmic voids

### 2015-06-19 RefereeResponse.md

Conceptual:
==

1. **It seems that part of the motivation for using FA is that it is
    very well correlated with lambda_1,  at low lambda_1. FA is a
    rather interesting quantity in itself, differentiating haloes and
    voids from  
    filaments and walls, but it is not clear why it should be superior to lambda_1 for void finding. The 
    authors should more clearly articulate why this might be, if there
    is a reason. The FA being "conceived  to quantify the anisotropy
    of the diffusivity of water molecules through cerebral tissue in
    nuclear  magnetic resonance imaging" should be elaborated on; this
    does not clarify the usefulness of the FA for
    cosmologists. Conceptually, I also wonder: do filaments and walls
    behave differently from each other in  FA, or do they both have FA
    ~ 1?**

      Response: 
      - Although lambda_1 is the defining property of voids when using
      the FA has a key advantage that makes it a better void tracer,
      namely that it is possible to define a boundary in regions with
      FA~1. The boudary setting is more arbitrary in the case of using
      lambda_1 as a tracer. We make this clarification in the 
	3rd paragraph of subsec. 3.2 of the new version.
      - Now it is explicitly explained why the FA, as defined in the
      context of MRI, is useful to cosmologist  
	(6th paragraph of introduction and 1st paragraph of subsec 3.1).
      - A new figure (Fig 3.) was prepared. Histograms of the volume
      contribution of each environment for  
	each value of the FA (3rd paragraph of subsec. 3.2). Sheets
      (mainly) and filaments are clearly  
	associated with high values of the FA.

@@

2. **I did not understand the sentence at the end of Sect 2, "In this
    work we propose an optimal value of  the threshold based on the
    maximization of the fractional anisotropy field in the locations
    label[ed]  as filaments and walls," and this seems to be an important point. Is the threshold mentioned in this 
    sentence a threshold in lambda_1, or FA? Is this the 0.95
    threshold in FA? It seems to be a reasonable choice, but I do not
    see a sense in which it is "optimal," except that it seems to be
    the boundary  between the FA being well-correlated with lambda_1
    and not-so-well. Also, if this sentence is about the     0.95
    threshold, I do not see why it "does not enter into our
    computations," since the boundary of many    voids will depend on
    this threshold. It would be useful to know for what fraction of
    voids the limit    FA = 0.95 actually affects the boundary (in the
    case of the largest voids, I suppose).**

    Response:
    We have rewritten this paragraph. The threshold that is not
    relevant to our computations is lambda_th, not FA=0.95.

### 2015-06-19 cosmic_voids.tex
removed new figure 3, removed before-after

\before{ The tracer that we use to define the 
voids is the fractional anisotropy (FA) computed from the set of 
eigenvalues of the tensor under consideration. 
The FA was initially introduced by \citet{Basser95} to quantify the
anisotropy degree of the diffusivity of water molecules through
cerebral tissue in nuclear magnetic resonance
imaging and \citet{Libeskind13} introduced this concept in the context
of Cosmic Web classification schemes.}

\after{The tracer that we use to define the voids is the fractional
anisotropy (FA) computed from the set of eigenvalues of the tensor
under consideration. 
The FA was initially introduced by \citet{Basser95} to quantify the
anisotropy degree of the diffusivity of water molecules through
cerebral tissue in nuclear magnetic resonance imaging, thereby allowing to 
detect structures that restrict the otherwise isotropic Brownian movement 
of water molecules. Taking into account that this process is identical to 
the velocity shear in the large-scale matter distribution, 
\citet{Libeskind13} introduced the concept of the FA in the context of 
Cosmic Web classification schemes.}

@@

%-------------------------------------------------------------------------
%FIGURE 3: Histograms for each environment regarding the FA value
\begin{figure}
\centering

  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.35\textheight]{FA_environment.pdf}

  \captionof{figure}{\small Volume of each environment per FA 
  ($dV_i/dFA,\ \ i=v,s,f,k$) normalized by the total volume per FA ($dV/dFA$).
  Top/bottom corresponds to the T-Web/V-Web. For a given value of the FA, 
  each line represents the volume contribution of the respective 
  environment to the total volume with the same FA value. Above FA=0.95,
  only sheets and filaments contribute to all the volume of the simulation
  within that range of FA.}
  \label{fig:FA_environment}

\end{figure}
%.........................................................................

@@

\before{The fractional anisotropy (FA), as developed by \citet{Basser95}, was 
conceived to quantify the anisotropy of the diffusivity of water
molecules through cerebral tissue in nuclear magnetic resonance imaging. 
Here we present the FA, much in the same way as \citet{Libeskind13},
to use it as a tracer of cosmic voids.}

\after{The fractional anisotropy (FA), as developed by \citet{Basser95}, 
was conceived to quantify the anisotropy of the diffusivity of water
molecules through cerebral tissue in nuclear magnetic resonance imaging. 
In this manner, barriers such as microtubules and cell membranes, that 
restrict the otherwise isotropic Brownian motion of water molecules, can 
be detected. In a cosmological context, the problem of finding structures 
is very similar, where filaments and sheets restrict the otherwise 
isotropic collapsing/expanding dynamics of the matter. Taking this into 
account, we present here the FA, much in the same way as \citet{Libeskind13}, 
to use it as a tracer of cosmic voids.}

@@

% CORRECTION !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
\before{In Fig. \ref{fig:L1_correlations} we show that the these two values
are indeed closely correlated.  
The right panel shows the correlation between $\lambda_1$ and $\delta$ for
all the grid cells in the simulation while the right panel shows the
correlation between $\lambda_1$ and the FA. This shows that the
overdensity has a large scatter at fixed $\lambda_1$.}

\after{In Fig. \ref{fig:L1_correlations} we show that the these two values
are indeed closely correlated.  The top panel shows the correlation between 
$\lambda_1$ and $\delta$ for all the grid cells in the simulation while the 
bottom panel shows the correlation between $\lambda_1$ and the FA. The middle 
panel shows the correlation between $\delta$ and the FA. This shows that the 
density has a larger scatter at fixed $\lambda_1$ than the FA, yet large and 
small values of the density remain still associated to low values of the FA.}

\after{At this point, the eigenvalue $\lambda_1$ and the FA appear to be
equally potential candidates for tracing cosmic voids, however, the 
eigenvalue $\lambda_1$ presents, along with the density, an undesirable 
feature for a void tracer. As we move out from inner parts of voids to outer 
parts, $\lambda_1$ and the density increase monotonically, making unclear 
where to set the frontier of voids. On the other hand, the FA naturally 
indicates the real frontier as regions where anisotropic collapse begin to 
dominate, which, according to Fig. \ref{fig:FA_environment}, are associated
mainly to sheets and, to a lesser extent, to filaments.}
%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

@@

However, there are two main differences in our approach with respect to other
watershed implementations.
First, the watershed technique commonly uses the density field
instead of the FA field as we do here
\citep{Platen07,Neyrinck08}.   
Second, we estimate all relevant quantities on a Cartesian mesh of
fixed cell size, while other works use an adaptive Delaunay tessellation
\citep{Schaap00}.
\before{However, from the analysis of our results the choice of a fixed
Cartesian mesh does not induce spurious results, at least with
the mass resolution we have in the N-body simulation. }
\after{Nevertheless, in our case the average number of particles per cell
  is large enough ($512$ particles/cell) ensuring that the lowest
  density regions are sampled with at least $\sim 10$ particles
  ($\delta \sim-0.98$), which seems to avoid spurious results from a
  noisy density field sampling.}

% CORRECTION !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
\before{The watershed algorithm also needs a threshold value to reduce
spurious features and prevent void hierarchization.  
If the density field is used, a typical threshold is
$\delta = -0.8$ \citep{Platen07},  which means that any ridge between
two voids with overdensity below that value is removed to merge the
respective voids. 
In our case we have to find a corresponding FA value
to define this threshold.}

\after{The watershed algorithm also needs a threshold value to reduce
spurious features and prevent void hierarchization.  
If the density field is used, a typical threshold is
$\delta = -0.8$ \citep{Platen07},  which means that, given two neighbouring 
voids, if the mean value of the density across their common boundary is 
below that threshold, the two voids are merged.
In our case we have to find a corresponding FA value
to define this threshold.}
%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

@@

We limit our results to voids with effective radius larger than the
smoothing length of the density field, i.e. $\sim 1$\hMpc.  
\before{Below that scale numerical resolution effects become
  important. }
\after{For smaller interpolation/smoothing scales the shot noise in
  the low density regions starts to be noticeable.}
With that choice we find a void volume filling fraction $54.88\%$ and
$47.06\%$ for the FA-Vweb and the FA-Tweb, respectively.  
\after{For larger smoothing scales ($>5\hMpc$) the density and shear fields
  tend to be Gaussian and therefore follow closely the analytical environment abundance
  predictions for Gaussian random fields \citep{Forero09,Alonso2015}. }

@@

\before{We find that subcompensated voids have outflowing velocity profiles
all the way up to the effective radius where the average radial
density reaches the average value.}
\after{We find that subcompensated voids have outflowing velocity profiles
all the way up to the radius where the average radial
density reaches the average value.}
For voids with sizes $\reff <8\hMpc$ the outflow is always
positive, consistent with the fact that their density profiles do not
reach the level $\delta=0$ in the range of explored radii.
This behaviour indicates that matter is being pulled out of the void
into external higher density features.

>>>>

The tracer that we use to define the voids is the fractional
anisotropy (FA) computed from the set of eigenvalues of the tensor
under consideration. 
The FA was initially introduced by \citet{Basser95} to quantify the
anisotropy degree of the diffusivity of water molecules through
cerebral tissue in nuclear magnetic resonance imaging, thereby allowing to 
detect structures that restrict the otherwise isotropic Brownian movement 
of water molecules. Taking into account that this process is identical to 
the velocity shear in the large-scale matter distribution, 
\citet{Libeskind13} introduced the concept of the FA in the context of 
Cosmic Web classification schemes.

@@

%-------------------------------------------------------------------------
%FIGURE 3: Histograms for each environment regarding the FA value
%\begin{figure}
%\centering
%  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
%  width=0.35\textheight]{FA_environment.pdf}
%   \captionof{figure}{\small Volume of each environment per FA
%   ($dV_i/dFA,\ \ i=v,s,f,k$) normalized by the total volume per FA
%   ($dV/dFA$). 
%  Top/bottom corresponds to the T-Web/V-Web. For a given value of the FA, 
%  each line represents the volume contribution of the respective 
%  environment to the total volume with the same FA value. Above FA=0.95,
%  only sheets and filaments contribute to all the volume of the simulation
%  within that range of FA.}
%  \label{fig:FA_environment}
%\end{figure}
%.........................................................................

@@

The fractional anisotropy (FA), as developed by \citet{Basser95}, 
was conceived to quantify the anisotropy of the diffusivity of water
molecules through cerebral tissue in nuclear magnetic resonance imaging. 
In this manner, barriers such as microtubules and cell membranes, that 
restrict the otherwise isotropic Brownian motion of water molecules, can 
be detected. In a cosmological context, the problem of finding structures 
is very similar, where filaments and sheets restrict the otherwise 
isotropic collapsing/expanding dynamics of the matter. Taking this into 
account, we present here the FA, much in the same way as \citet{Libeskind13}, 
to use it as a tracer of cosmic voids.

@@

In Fig. \ref{fig:L1_correlations} we show that the these two values
are indeed closely correlated.  The top panel shows the correlation between 
$\lambda_1$ and $\delta$ for all the grid cells in the simulation while the 
bottom panel shows the correlation between $\lambda_1$ and the FA. The middle 
panel shows the correlation between $\delta$ and the FA. This shows that the 
density has a larger scatter at fixed $\lambda_1$ than the FA, yet large and 
small values of the density remain still associated to low values of the FA.

At this point, the eigenvalue $\lambda_1$ and the FA appear to be
equally potential candidates for tracing cosmic voids, however, the 
eigenvalue $\lambda_1$ presents, along with the density, an undesirable 
feature for a void tracer. As we move out from inner parts of voids to outer 
parts, $\lambda_1$ and the density increase monotonically, making unclear 
where to set the frontier of voids. On the other hand, the FA naturally 
indicates the real frontier as regions where anisotropic collapse begin to 
dominate, which, according to Fig. \ref{fig:FA_environment}, are associated
mainly to sheets and, to a lesser extent, to filaments.
%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

@@

However, there are two main differences in our approach with respect to other
watershed implementations.
First, the watershed technique commonly uses the density field
instead of the FA field as we do here
\citep{Platen07,Neyrinck08}.   
Second, we estimate all relevant quantities on a Cartesian mesh of
fixed cell size, while other works use an adaptive Delaunay tessellation
\citep{Schaap00}.
Nevertheless, in our case the average number of particles per cell
  is large enough ($512$ particles/cell) ensuring that the lowest
  density regions are sampled with at least $\sim 10$ particles
  ($\delta \sim-0.98$), which seems to avoid spurious results from a
  noisy density field sampling.

The watershed algorithm also needs a threshold value to reduce
spurious features and prevent void hierarchization.  
If the density field is used, a typical threshold is
$\delta = -0.8$ \citep{Platen07},  which means that, given two neighbouring 
voids, if the mean value of the density across their common boundary is 
below that threshold, the two voids are merged.
In our case we have to find a corresponding FA value
to define this threshold.
%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

@@

We limit our results to voids with effective radius larger than the
smoothing length of the density field, i.e. $\sim 1$\hMpc.  
For smaller interpolation/smoothing scales the shot noise in
  the low density regions starts to be noticeable.
With that choice we find a void volume filling fraction $54.88\%$ and
$47.06\%$ for the FA-Vweb and the FA-Tweb, respectively.  
For larger smoothing scales ($>5\hMpc$) the density and shear fields
  tend to be Gaussian and therefore follow closely the analytical environment abundance
  predictions for Gaussian random fields \citep{Forero09,Alonso2015}.

@@

We find that subcompensated voids have outflowing velocity profiles
all the way up to the radius where the average radial
density reaches the average value.
For voids with sizes $\reff <8\hMpc$ the outflow is always
positive, consistent with the fact that their density profiles do not
reach the level $\delta=0$ in the range of explored radii.
This behaviour indicates that matter is being pulled out of the void
into external higher density features.
